Fontawesome

### 2022-07-19 Shiny/Test/Flexdashboard rows.Rmd
Icon tests.

    # Duplicate value boxes for testing
    output$KPI_box2 <- renderValueBox({
      valueBox(
        value = KPI_admin(),
        caption = "danger",
        color = "danger",
        icon = "fa-random"
      )
    })
    output$KPI_box3 <- renderValueBox({
      valueBox(
        value = KPI_admin(),
        caption = "success",
        color = "success",
        icon = "fa-random"
      )
    })

    output$KPI_box4 <- renderValueBox({
      valueBox(
        value = KPI_admin(),
        caption = "info",
        color = "info",
        icon = "fa-random"
      )})

>>>>

    # Duplicate value boxes for testing
    output$KPI_box2 <- renderValueBox({
      valueBox(
        value = KPI_admin(),
        caption = "danger",
        color = "danger",
        icon = "fas fa-dog"
      )
    })
    output$KPI_box3 <- renderValueBox({
      valueBox(
        value = KPI_admin(),
        caption = "success",
        color = "success",
        icon = "fas fa-coffee"
      )
    })

    output$KPI_box4 <- renderValueBox({
      valueBox(
        value = KPI_admin(),
        caption = "info",
        color = "info",
        icon = "fas fa-skull-and-crossbones"
      )})

### 2022-07-19 Shiny/Test/Fontawesome.Rmd
Icon tests.

```{r}
# Creating df
df <- fontawesome::fa_metadata()
# Version check
df$version
# Example search
df$icon_names_full |> str_view_all("battery", match = TRUE)
```

>>>>

```{r}
# Creating df
df <- fontawesome::fa_metadata()
# Version check
df$version
# Example search
df$icon_names_full |> str_view_all("skull", match = TRUE)
```
